---
header-includes:
- \usepackage{hyperref}
- \usepackage{graphicx}
- \graphicspath{{stat-tables_files/figure-latex/}}
- \usepackage{geometry}
- \geometry{a4paper,left=.6in,right=.6in,top=1in,bottom=1in}
output:
  pdf_document:
    keep_tex: yes
---

```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
library(kableExtra)
library(iprior)
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, fig.path = "figure/", 
                      cache.path = "_cache/", fig.width = 9, fig.height = 5)
```

\thispagestyle{empty}
\begin{center}
~\\
\vspace{2cm}
{\Huge Statistical Tables}
~\\~\\
v0.2 (last updated: 12 Feb 2021)
\vspace{5cm}
\end{center}

```{r, fig.height = 3, fig.width = 6,out.width = "\\textwidth", warning = FALSE, fig.align = "center"}
x <- seq(-3, 3, length = 3000)
y <- dnorm(x)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  # geom_line() +
  geom_ribbon(aes(ymax = y, ymin = 0), alpha = 0.5, col = NA) +
  geom_col(aes(fill = x)) +
  scale_fill_gradientn(colours = iprior::gg_col_hue(10)[c(4:10, 1:3)]) +
  theme_void() +
  theme(legend.position = "none")
```

\vfill
\begin{center}
Copyright (c) 2020--present Haziq Jamil
~\\
\href{https://haziqj.github.io/stat-tables}{\texttt{https://haziqj.github.io/stat-tables}}
\end{center}

\newpage

### Table 1: Cumulative probabilities of the standard normal distribution.

Each table entry is the area $A=1-\alpha$ under the standard normal curve from $-\infty$ to $z(\alpha)$.
That is, the entries are $\int_{-\infty}^{z(\alpha)}f_Z(z) \, dz = A = 1-\alpha$, where $f_Z$ is the pdf of $Z\sim \text{N}(0,1)$.

\vspace{1em}

```{r, fig.height = 3, fig.width = 6,out.width = "6cm", warning = FALSE, fig.align = "center"}
x <- seq(-3, 3, length = 200)
y <- dnorm(x)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  geom_line() +
  geom_ribbon(data = subset(dat , x >= -3 & x <= 0.8), aes(ymax = y),
              ymin = 0, fill = iprior::gg_col_hue(1), colour = NA,
              alpha = 0.5) +
  geom_line(data = tibble(xx = c(0.8, 0.8), yy = c(0, dnorm(0.8))),
            aes(xx, yy), linetype = "dashed") +
  # annotate("text", x = -0.25, y = 0.17, size = 5, 
  #          label = expression("A ="~P (Z<z[alpha]) )  ) +
  annotate("text", x = -0.25, y = 0.17, size = 8, label = "A") +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks = 0.8, labels = expression(z(alpha))) +
  theme_classic() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 20))
```

```{r normtab}
u <- seq(0, 3.49 , by = 0.01)
p <- pnorm(u)
m <- data.frame(matrix(p, ncol = 10, byrow = TRUE))
colnames(m) <- c(
  gsub("0.0", ".0", iprior::dec_plac(seq(0, 0.09, by = 0.01), 2))
)
rownames(m) <- c(
  iprior::dec_plac(seq(0, 3.4, by = 0.1), 1)
)
m <- cbind("$z$" = rownames(m), m)

options(digits = 4)
kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE) %>%
  kable_styling(position = "center")
```

\newpage
### Table 2: Percentiles of the $\chi^2$-distribution.

Each table entry is $\chi^2_k(\alpha)$, where $\int_{0}^{\chi^2_k(\alpha)}f_X(x) \, dx = A = 1-\alpha$ with $X\sim\chi^2_k$.

```{r, fig.height = 2.7, fig.width = 6, out.width = "6cm", warning = FALSE, fig.align = "center"}
x <- seq(0, 10, length = 250)
y <- dchisq(x, df = 3.3)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  geom_line() +
  geom_ribbon(data = subset(dat , x <= 6), aes(ymax = y),
              ymin = 0, fill = iprior::gg_col_hue(1), colour = NA,
              alpha = 0.5) +
  geom_line(data = tibble(xx = c(6, 6), yy = c(0, dchisq(6, 3.3))),
            aes(xx, yy), linetype = "dashed") +
  annotate("text", x = 2.3, y = 0.08, size = 8, label = "A") +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks = c(0, 6), 
                     labels = c(0, expression(chi[k]^2 ~(alpha)))) +
  theme_classic() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 20))
```

```{r chisqtab}
u <- c(0.005, 0.010, 0.025, 0.050, 0.100, 0.900, 0.950, 0.975, 0.990, 0.995)
k <- c(seq(1, 29, by = 1), seq(30, 100, by = 10))
m <- data.frame(matrix(NA, ncol = length(u), nrow = length(k)))
for (i in seq_along(k)) {
  m[i, ] <- qchisq(u, df = k[i])
}
colnames(m) <- iprior::dec_plac(u, 3)
# rownames(m) <- k
m <- cbind("$k$" = k, iprior::dec_plac(m, 3))
m[1, 2] <- "$0.0^4393$"
m[1, 3] <- "$0.0^3157$"
m[1, 4] <- "$0.0^3982$"
m[1, 5] <- "$0.0^2393$"
# m[1, 6] <- "$0.0158$"

options(digits = 4)
kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE, 
      align = c("l", rep("r", length(u)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$A$" = 10), escape = FALSE)
```

\newpage
### Table 3: Percentiles of Student's $t$-distribution.

Each table entry is $t_k(\alpha)$, where $\int_{-\infty}^{t_k(\alpha)}f_X(x) \, dx = A = 1-\alpha$ with $X\sim t_k$.



```{r, fig.height = 3, fig.width = 6,out.width = "6cm", warning = FALSE, fig.align = "center"}
x <- seq(-3, 3, length = 200)
y <- dt(x, df = 1)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  geom_line() +
  geom_ribbon(data = subset(dat , x >= -3 & x <= 0.8), aes(ymax = y),
              ymin = 0, fill = iprior::gg_col_hue(1), colour = NA,
              alpha = 0.5) +
  geom_line(data = tibble(xx = c(0.8, 0.8), yy = c(0, dt(0.8, 1))),
            aes(xx, yy), linetype = "dashed") +
  annotate("text", x = -0.25, y = 0.13, size = 8, label = "A") +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks = 0.8, labels = expression(t[k]~(alpha) )) +
  theme_classic() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 20))
```

```{r ttab}
u <- c(0.60, 0.70, 0.80, 0.85, 0.90, 0.95, 0.975, 0.99, 0.9925, 0.995, 0.9975, 0.9995)
k <- c(seq(1, 30, by = 1), c(40, 60, 120, Inf))
m <- data.frame(matrix(NA, ncol = length(u), nrow = length(k)))
for (i in seq_along(k)) {
  m[i, ] <- qt(u, df = k[i])
}
colnames(m) <- c(
  iprior::dec_plac(c(0.60, 0.70, 0.80, 0.85, 0.90, 0.95), 2),
  iprior::dec_plac(c(0.975, 0.99), 3),
  iprior::dec_plac(c(0.9925, 0.995, 0.9975, 0.9995), 4)
)
m <- cbind("$k$" = k, iprior::dec_plac(m, 3))
m[nrow(m), 1] <- "$\\infty$"

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE, 
      align = c("l", rep("r", length(u)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$A$" = length(u)), escape = FALSE)
```

\newpage
### Table 4.1: Percentiles of the $F$-distribution.

Each table entry is $F_{k_1,k_2}(\alpha) = F_{k_2,k_1}^{-1}(1-\alpha)$, where $\int_{-\infty}^{F_{k_1,k_2}(\alpha)}f_X(x) \, dx = A = 1-\alpha$ with $X\sim F_{k_1,k_2}$.

```{r, fig.height = 2.6, fig.width = 6,out.width = "6cm", warning = FALSE, fig.align = "center"}
x <- seq(0, 10, length = 250)
y <- df(x, df1 = 10, df2 = 2)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  geom_line() +
  geom_ribbon(data = subset(dat , x <= 6), aes(ymax = y),
              ymin = 0, fill = iprior::gg_col_hue(1), colour = NA,
              alpha = 0.5) +
  geom_line(data = tibble(xx = c(6, 6), yy = c(0, df(6, 10, 2))),
            aes(xx, yy), linetype = "dashed") +
  annotate("text", x = 1.3, y = 0.1, size = 8, label = "A") +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks = c(0, 6), 
                     labels = c(0, expression(F[k[1]~","~k[2]] ~(alpha)))) +
  theme_classic() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 20))
```


```{r ftab1}
u <- c(0.5, 0.9, 0.95, 0.975, 0.99, 0.995, 0.999)
k1 <- 1:10
k2 <- 1:5
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 1
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 1)
m[3:7, ] <- round(tmp[3:7, ])

# k2 = 2
m[8:9, ]   <- iprior::dec_plac(tmp[8:9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 2)

# k2 = 3
m[15:17, ] <- iprior::dec_plac(tmp[15:17, ], 3)
m[18:19, ] <- iprior::dec_plac(tmp[18:19, ], 2)
m[20:21, ] <- iprior::dec_plac(tmp[20:21, ], 1)

# k2 = 4
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:25, ] <- iprior::dec_plac(tmp[23:25, ], 2)
m[26:28, ] <- iprior::dec_plac(tmp[26:28, ], 1)

# k2 = 5
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:32, ] <- iprior::dec_plac(tmp[30:32, ], 2)
m[33:35, ] <- iprior::dec_plac(tmp[33:35, ], 1)

colnames(m) <- k1
m <- cbind("\\hspace{1.1em}$A$" = rep(as.character(u), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=1$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=2$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=3$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=4$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=5$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.2: (Continued) Percentiles of the $F$-distribution.

```{r ftab2}
u <- c(0.5, 0.9, 0.95, 0.975, 0.99, 0.995, 0.999)
k1 <- c(11, 12, 13, 14, 15, 20, 30, 60, 120, Inf)
k2 <- 1:5
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 1
m[1, ] <- iprior::dec_plac(tmp[1, ], 2)
m[2, ] <- iprior::dec_plac(tmp[2, ], 1)
m[3:7, ] <- round(tmp[3:7, ])

# k2 = 2
m[8:9, ]   <- iprior::dec_plac(tmp[8:9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 2)

# k2 = 3
m[15:17, ] <- iprior::dec_plac(tmp[15:17, ], 3)
m[18:19, ] <- iprior::dec_plac(tmp[18:19, ], 2)
m[20:21, ] <- iprior::dec_plac(tmp[20:21, ], 1)

# k2 = 4
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:25, ] <- iprior::dec_plac(tmp[23:25, ], 2)
m[26:28, ] <- iprior::dec_plac(tmp[26:28, ], 1)

# k2 = 5
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:32, ] <- iprior::dec_plac(tmp[30:32, ], 2)
m[33:35, ] <- iprior::dec_plac(tmp[33:35, ], 1)

colnames(m) <- k1
colnames(m)[10] <- "$\\infty$"
m <- cbind("\\hspace{1.1em}$A$" = rep(as.character(u), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=1$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=2$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=3$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=4$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=5$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.3: (Continued) Percentiles of the $F$-distribution.

```{r ftab3}
u <- c(0.5, 0.9, 0.95, 0.975, 0.99, 0.995, 0.999)
k1 <- 1:10
k2 <- 6:10
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15, ] <- iprior::dec_plac(tmp[15, ], 3)
m[16:21, ] <- iprior::dec_plac(tmp[16:21, ], 3)

# k2 = 9
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:28, ] <- iprior::dec_plac(tmp[23:28, ], 3)

# k2 = 10
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:35, ] <- iprior::dec_plac(tmp[30:35, ], 3)

colnames(m) <- k1
m <- cbind("\\hspace{1.1em}$A$" = rep(as.character(u), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=6$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=7$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=8$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=9$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=10$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.4: (Continued) Percentiles of the $F$-distribution.

```{r ftab4}
u <- c(0.5, 0.9, 0.95, 0.975, 0.99, 0.995, 0.999)
k1 <- c(11, 12, 13, 14, 15, 20, 30, 60, 120, Inf)
k2 <- 6:10
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15, ] <- iprior::dec_plac(tmp[15, ], 3)
m[16:21, ] <- iprior::dec_plac(tmp[16:21, ], 3)

# k2 = 9
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:28, ] <- iprior::dec_plac(tmp[23:28, ], 3)

# k2 = 10
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:35, ] <- iprior::dec_plac(tmp[30:35, ], 3)

colnames(m) <- k1
colnames(m)[10] <- "$\\infty$"
m <- cbind("\\hspace{1.1em}$A$" = rep(as.character(u), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=6$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=7$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=8$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=9$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=10$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.5: (Continued) Percentiles of the $F$-distribution.

```{r ftab5}
u <- c(0.5, 0.9, 0.95, 0.975, 0.99, 0.995, 0.999)
k1 <- 1:10
k2 <- c(11, 12, 13, 14, 15)
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15, ] <- iprior::dec_plac(tmp[15, ], 3)
m[16:21, ] <- iprior::dec_plac(tmp[16:21, ], 3)

# k2 = 9
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:28, ] <- iprior::dec_plac(tmp[23:28, ], 3)

# k2 = 10
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:35, ] <- iprior::dec_plac(tmp[30:35, ], 3)

colnames(m) <- k1
m <- cbind("\\hspace{1.1em}$A$" = rep(as.character(u), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=11$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=12$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=13$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=14$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=15$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.6: (Continued) Percentiles of the $F$-distribution.

```{r ftab6}
u <- c(0.5, 0.9, 0.95, 0.975, 0.99, 0.995, 0.999)
k1 <- c(11, 12, 13, 14, 15, 20, 30, 60, 120, Inf)
k2 <- c(11, 12, 13, 14, 15)
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15:16, ] <- iprior::dec_plac(tmp[15:16, ], 3)
m[17:21, ] <- iprior::dec_plac(tmp[17:21, ], 3)

# k2 = 9
m[22:23, ] <- iprior::dec_plac(tmp[22:23, ], 3)
m[24:28, ] <- iprior::dec_plac(tmp[24:28, ], 3)

# k2 = 10
m[29:30, ] <- iprior::dec_plac(tmp[29:30, ], 3)
m[31:35, ] <- iprior::dec_plac(tmp[31:35, ], 3)

colnames(m) <- k1
colnames(m)[10] <- "$\\infty$"
m <- cbind("\\hspace{1.1em}$A$" = rep(as.character(u), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=11$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=12$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=13$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=14$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=15$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.7: (Continued) Percentiles of the $F$-distribution.

```{r ftab7}
u <- c(0.5, 0.9, 0.95, 0.975, 0.99, 0.995, 0.999)
k1 <- 1:10
k2 <- c(20, 30, 60, 120, Inf)
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15, ] <- iprior::dec_plac(tmp[15, ], 3)
m[16:21, ] <- iprior::dec_plac(tmp[16:21, ], 3)

# k2 = 9
m[22, ] <- iprior::dec_plac(tmp[22, ], 3)
m[23:28, ] <- iprior::dec_plac(tmp[23:28, ], 3)

# k2 = 10
m[29, ] <- iprior::dec_plac(tmp[29, ], 3)
m[30:35, ] <- iprior::dec_plac(tmp[30:35, ], 3)

colnames(m) <- k1
m <- cbind("\\hspace{1.1em}$A$" = rep(as.character(u), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=20$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=30$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=60$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=120$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=\\infty$", 29, 35, escape = FALSE)
```

\newpage
### Table 4.8: (Continued) Percentiles of the $F$-distribution.

```{r ftab8}
u <- c(0.5, 0.9, 0.95, 0.975, 0.99, 0.995, 0.999)
k1 <- c(11, 12, 13, 14, 15, 20, 30, 60, 120, Inf)
k2 <- c(20, 30, 60, 120, Inf)
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 6
m[1, ] <- iprior::dec_plac(tmp[1, ], 3)
m[2, ] <- iprior::dec_plac(tmp[2, ], 3)
m[3:7, ] <- iprior::dec_plac(tmp[3:7, ], 3)

# k2 = 7
m[8, ]   <- iprior::dec_plac(tmp[8, ], 3)
m[9, ]   <- iprior::dec_plac(tmp[9, ], 3)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 3)

# k2 = 8
m[15:16, ] <- iprior::dec_plac(tmp[15:16, ], 3)
m[17:21, ] <- iprior::dec_plac(tmp[17:21, ], 3)

# k2 = 9
m[22:23, ] <- iprior::dec_plac(tmp[22:23, ], 3)
m[24:28, ] <- iprior::dec_plac(tmp[24:28, ], 3)

# k2 = 10
m[29:30, ] <- iprior::dec_plac(tmp[29:30, ], 4)
m[31:35, ] <- iprior::dec_plac(tmp[31:35, ], 4)

colnames(m) <- k1
colnames(m)[10] <- "$\\infty$"
m <- cbind("\\hspace{1.1em}$A$" = rep(as.character(u), length(k2)), m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  # collapse_rows(1, latex_hline = "none", row_group_label_position = "stack")
  pack_rows("$k_2=20$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=30$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=60$", 15, 21, escape = FALSE) %>%
  pack_rows("$k_2=120$", 22, 28, escape = FALSE) %>%
  pack_rows("$k_2=\\infty$", 29, 35, escape = FALSE, bold = FALSE)
```

\newpage
### Table 5: Binomial probabilities

The entries in the binomial tables are $\Pr(X=x)$ where $X\sim\text{Bin}(n,p)$.

```{r binomtab1}
prob <- c(0.01, 0.05, seq(0.1, 0.9, by = 0.1), 0.95, 0.99)
n <- 2:8
nlist <- xlist <- list()
for (i in seq_along(n)) {
  xlist[[i]] <- 0:(n[i])
  nlist[[i]] <- rep(n[i], length(xlist[[i]]))
}

tab <- data.frame(
  n = unlist(nlist),
  x = unlist(xlist)
)
for (i in seq_along(prob)) {
  tab <- cbind(tab, dbinom(tab$x, tab$n, prob[i]))
}
colnames(tab) <- c("n", "$\\hspace{1em}x$", prob)

kable(tab[, -1], booktabs = TRUE, row.names = FALSE, escape = FALSE, digits = 3,
      align = c("l", rep("r", length(prob)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$p$" = length(prob)), escape = FALSE) %>%
  pack_rows("$n=2$", 1, 3, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=3$", 4, 7, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=4$", 8, 12, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=5$", 13, 18, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=6$", 19, 25, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=7$", 26, 33, escape = FALSE, bold = FALSE) %>%
  pack_rows("$n=8$", 34, 42, escape = FALSE, bold = FALSE)
```

```{r binomtab2}
prob <- c(0.01, 0.05, seq(0.1, 0.9, by = 0.1), 0.95, 0.99)
n <- 9:12
nlist <- xlist <- list()
for (i in seq_along(n)) {
  xlist[[i]] <- 0:(n[i])
  nlist[[i]] <- rep(n[i], length(xlist[[i]]))
}

tab <- data.frame(
  n = unlist(nlist),
  x = unlist(xlist)
)
for (i in seq_along(prob)) {
  tab <- cbind(tab, dbinom(tab$x, tab$n, prob[i]))
}
colnames(tab) <- c("n", "$\\hspace{1em}x$", prob)

kable(tab[, -1], booktabs = TRUE, row.names = FALSE, escape = FALSE, digits = 3,
      align = c("l", rep("r", length(prob)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$p$" = length(prob)), escape = FALSE) %>%
  pack_rows("$n=9$", 1, 5, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 6, 10, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=10$", 11, 15, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 16, 20, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 21, 21, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=11$", 22, 26, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 27, 31, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 32, 33, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%  
  pack_rows("$n=12$", 34, 38, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 39, 43, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 44, 46, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") 
```


```{r binomtab3}
prob <- c(0.01, 0.05, seq(0.1, 0.9, by = 0.1), 0.95, 0.99)
n <- 13:15
nlist <- xlist <- list()
for (i in seq_along(n)) {
  xlist[[i]] <- 0:(n[i])
  nlist[[i]] <- rep(n[i], length(xlist[[i]]))
}

tab <- data.frame(
  n = unlist(nlist),
  x = unlist(xlist)
)
for (i in seq_along(prob)) {
  tab <- cbind(tab, dbinom(tab$x, tab$n, prob[i]))
}
colnames(tab) <- c("n", "$\\hspace{1em}x$", prob)

kable(tab[, -1], booktabs = TRUE, row.names = FALSE, escape = FALSE, digits = 3,
      align = c("l", rep("r", length(prob)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$p$" = length(prob)), escape = FALSE) %>%
  pack_rows("$n=13$", 1, 5, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 6, 10, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 11, 14, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=14$", 15, 19, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 20, 24, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 25, 29, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows("$n=15$", 30, 34, escape = FALSE, bold = FALSE) %>%
  pack_rows(" ", 35, 39, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%
  pack_rows(" ", 40, 44, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") %>%  
  pack_rows(" ", 45, 45, escape = FALSE, bold = FALSE, latex_gap_space = "-.7em") 
```
