---
# title: "Statistical Tables"
# author: "Haziq Jamil"
# date: "15/03/2020"
output: pdf_document
header-includes:
- \usepackage{hyperref}
---

```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
library(kableExtra)
library(iprior)
knitr::opts_chunk$set(echo = FALSE)
```

\thispagestyle{empty}
\begin{center}
~\\
\vspace{2cm}
{\Huge Statistical Tables}
\vspace{5cm}
\end{center}

```{r, fig.height = 3, fig.width = 6,out.width = "\\textwidth", warning = FALSE, fig.align = "center"}
x <- seq(-3, 3, length = 3000)
y <- dnorm(x)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  # geom_line() +
  geom_ribbon(aes(ymax = y, ymin = 0), alpha = 0.5, col = NA) +
  geom_col(aes(fill = x)) +
  scale_fill_gradientn(colours = iprior::gg_col_hue(10)[c(4:10, 1:3)]) +
  theme_void() +
  theme(legend.position = "none")
```

\vfill
\begin{center}
Copyright (c) 2020 Haziq Jamil
~\\
\href{https://github.com/haziqj/stat-tables}{\texttt{https://github.com/haziqj/stat-tables}}
\end{center}

\newpage

### Table 1: Cumulative probabilities of the standard normal distribution.

Each table entry is the area $A$ under the standard normal curve from $-\infty$ to $z(\alpha)$.

\vspace{1em}

```{r, fig.height = 3, fig.width = 6,out.width = "6cm", warning = FALSE, fig.align = "center"}
x <- seq(-3, 3, length = 200)
y <- dnorm(x)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  geom_line() +
  geom_ribbon(data = subset(dat , x >= -3 & x <= 0.8), aes(ymax = y),
              ymin = 0, fill = iprior::gg_col_hue(1), colour = NA,
              alpha = 0.5) +
  geom_line(data = tibble(xx = c(0.8, 0.8), yy = c(0, dnorm(0.8))),
            aes(xx, yy), linetype = "dashed") +
  # annotate("text", x = -0.25, y = 0.17, size = 5, 
  #          label = expression("A ="~P (Z<z[alpha]) )  ) +
  annotate("text", x = -0.25, y = 0.17, size = 8, label = "A") +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks = 0.8, labels = expression(z(alpha))) +
  theme_classic() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 20))
```

```{r normtab}
u <- seq(0, 3.49 , by = 0.01)
p <- pnorm(u)
m <- data.frame(matrix(p, ncol = 10, byrow = TRUE))
colnames(m) <- c(
  gsub("0.0", ".0", iprior::dec_plac(seq(0, 0.09, by = 0.01), 2))
)
rownames(m) <- c(
  iprior::dec_plac(seq(0, 3.4, by = 0.1), 1)
)

options(digits = 4)
kable(m, booktabs = TRUE) %>%
  kable_styling(position = "center")
```

### Table 2: Percentiles of the $\chi^2$ distribution.

Each table entry is $\chi^2_k(\alpha)$, where $\text{P}\big(X < \chi^2_k(\alpha)\big)=A$ with $X\sim\chi^2_k$.
\vspace{0.5em}
```{r, fig.height = 2.7, fig.width = 6, out.width = "6cm", warning = FALSE, fig.align = "center"}
x <- seq(0, 10, length = 250)
y <- dchisq(x, df = 3.3)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  geom_line() +
  geom_ribbon(data = subset(dat , x <= 6), aes(ymax = y),
              ymin = 0, fill = iprior::gg_col_hue(1), colour = NA,
              alpha = 0.5) +
  geom_line(data = tibble(xx = c(6, 6), yy = c(0, dchisq(6, 3.3))),
            aes(xx, yy), linetype = "dashed") +
  annotate("text", x = 2.3, y = 0.08, size = 8, label = "A") +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks = c(0, 6), 
                     labels = c(0, expression(chi[k]^2 ~(alpha)))) +
  theme_classic() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 20))
```

\vspace{-0.5em}

```{r chisqtab}
u <- c(0.005, 0.010, 0.025, 0.050, 0.100, 0.900, 0.950, 0.975, 0.990, 0.995)
k <- c(seq(1, 29, by = 1), seq(30, 100, by = 10))
m <- data.frame(matrix(NA, ncol = length(u), nrow = length(k)))
for (i in seq_along(k)) {
  m[i, ] <- qchisq(u, df = k[i])
}
colnames(m) <- iprior::dec_plac(u, 3)
# rownames(m) <- k
m <- cbind("$k$" = k, iprior::dec_plac(m, 3))
m[1, 2] <- "$0.0^4393$"
m[1, 3] <- "$0.0^3157$"
m[1, 4] <- "$0.0^3982$"
m[1, 5] <- "$0.0^2393$"
# m[1, 6] <- "$0.0158$"

options(digits = 4)
kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE, 
      align = c("l", rep("r", length(u)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$A$" = 10), escape = FALSE)
```

### Table 3: Percentiles of Student's $t$-distribution.

Each table entry is $t_k(\alpha)$, where $\text{P}\big(X < t_k(\alpha)\big)=A$ with $X\sim t_k$.

\vspace{1em}

```{r, fig.height = 3, fig.width = 6,out.width = "6cm", warning = FALSE, fig.align = "center"}
x <- seq(-3, 3, length = 200)
y <- dt(x, df = 1)
dat <- tibble(x, y)
ggplot(dat, aes(x, y)) +
  geom_line() +
  geom_ribbon(data = subset(dat , x >= -3 & x <= 0.8), aes(ymax = y),
              ymin = 0, fill = iprior::gg_col_hue(1), colour = NA,
              alpha = 0.5) +
  geom_line(data = tibble(xx = c(0.8, 0.8), yy = c(0, dt(0.8, 1))),
            aes(xx, yy), linetype = "dashed") +
  annotate("text", x = -0.25, y = 0.13, size = 8, label = "A") +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks = 0.8, labels = expression(t[k]~(alpha) )) +
  theme_classic() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 20))
```

```{r ttab}
u <- c(0.60, 0.70, 0.80, 0.85, 0.90, 0.95, 0.975, 0.99, 0.9925, 0.995, 0.9975, 0.9995)
k <- c(seq(1, 30, by = 1), c(40, 60, 120, Inf))
m <- data.frame(matrix(NA, ncol = length(u), nrow = length(k)))
for (i in seq_along(k)) {
  m[i, ] <- qt(u, df = k[i])
}
colnames(m) <- c(
  iprior::dec_plac(c(0.60, 0.70, 0.80, 0.85, 0.90, 0.95), 2),
  iprior::dec_plac(c(0.975, 0.99), 3),
  iprior::dec_plac(c(0.9925, 0.995, 0.9975, 0.9995), 4)
)
m <- cbind("$k$" = k, iprior::dec_plac(m, 3))
m[nrow(m), 1] <- "$\\infty$"

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE, 
      align = c("l", rep("r", length(u)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$A$" = length(u)), escape = FALSE)
```

### Table 3: Percentiles of the $F$-distribution.

```{r ftab}
u <- c(0.5, 0.9, 0.95, 0.975, 0.99, 0.995, 0.999)
k1 <- 1:10
k2 <- 1:3
uk2 <- expand.grid(u, k2)
m <- data.frame(matrix(NA, ncol = length(k1), nrow = nrow(uk2)))
for (i in seq_len(nrow(uk2))) {
  for (j in seq_along(k1)) {
    m[i, j] <- qf(uk2[i, 1], df1 = k1[j], df2 = uk2[i, 2])
  }
}
tmp <- m

# k2 = 1
m[1, ] <- iprior::dec_plac(tmp[1, ], 2)
m[2, ] <- iprior::dec_plac(tmp[2, ], 1)
m[3:7, ] <- round(tmp[3:7, ])

# k2 = 2
m[8:9, ]   <- iprior::dec_plac(tmp[8:9, ], 2)
m[10:14, ] <- iprior::dec_plac(tmp[10:14, ], 1)

# k2 = 3
m[15:17, ] <- iprior::dec_plac(tmp[15:17, ], 2)
m[18:21, ] <- iprior::dec_plac(tmp[18:21, ], 1)

colnames(m) <- k1
m <- cbind(" " = uk2[, 1], m)

kable(m, booktabs = TRUE, row.names = FALSE, escape = FALSE, digits = 3,
      align = c("l", rep("r", length(k1)))) %>%
  kable_styling(position = "center")  %>%
  add_header_above(c(" ", "$k_1$" = length(k1)), escape = FALSE) %>%
  pack_rows("$k_2=1$", 1, 7, escape = FALSE) %>%
  pack_rows("$k_2=2$", 8, 14, escape = FALSE) %>%
  pack_rows("$k_2=3$", 15, 21, escape = FALSE) 
```

